The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-03-25 papers/pair-correlation/paper.tex
rewrote abstract and added a jeffsays Tested on crystal. Took 0:37.07.

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We have developed an approximation for the pair distribution
  function of hard spheres, which is based on the average value of the
  pair distribution function at contact we recently developed.  Our
  pair distribution function is constructed so as to be computable
  with only single-site convolutions and to accurately reproduce the
  averaged distribution function at contact.  This results in a
  functional that is efficient to compute, and predicts the pair
  distribution function as well as the most accurate existing
  analytical approximation.  \davidsays{Jeff will rewrite this
    abstract.}
\end{abstract}

>>>>

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We introduce an approximation for the pair distribution function of
the inhomogeneous hard sphere fluid. Instead of relying on simple
convolutions of density, our approximation incorporates a radial
distribution function that is dependant upon a recently published
averaged pair distribution function at contact which has been shown to
give good results. We develop a separable form of this radial
distribution function that achieves greater computational efficiency
by allowing for the use of fast Fourier transforms. We compare results
for this separable version of our pair distribution approximation with
a Monte-Carlo based version, two previously published works, and
Monte-Carlo simulation, showing favorable results.  \jeffsays{In this
  I refer to the 'radial distribution function at contact'.  In the
  text (and in our previous paper) this is refered to using
  'correlation' versus 'distribution'.  I'm confused about how we
  switch back and forth in this paper.  Is it that we always refer to
  the contact pair function as correlation but the others as
  distribution?  Otherwise I didn't see any problems with the text.}
\end{abstract}
